\textit{Associations between chlorophyll \emph{a} and various microcystin-LR health advisory concentrations}

### 2016-01-25 manuscript/f1000_submission/manuscript.Rmd
version (almost) ready to submit to f1000

We used the 2007 NLA chlorophyll *a* and microcystin-LR concentration data [@usepa2009national, [NLA](http://www2.epa.gov/national-aquatic-resource-surveys/national-lakes-assessment)]. These data represent a snapshot of water quality from the summer of 2007 for the conterminous United States and were collected as part of an ongoing probabilistic monitoring program [@usepa2009national]. Data on chlorophyll *a* and microcystin-LR concentrations are available for `r nrow(na.omit(nla_dat$CHLA,nla_dat$MCYST_TL_UGL))` lakes.

@@

```{r epa_child_cp_plot, echo=FALSE, fig.width=6, fig.cap="",warning=FALSE,message=FALSE}
jpeg(filename = "hollister_microcystin_fig2.jpg",
       res = 450,
       width = 7.82,
       height = 6.8,
       units = "in")
multiplot(
  plot_cp(epa_child_cp,x = "Log 10 Chlorophyll", 
          y = "Conditional Probability",
          title="A."),
  plot_cp(who_drink_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="B."),
  plot_cp(epa_adult_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="C."),
  plot_cp(who_rec_low1_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="D."),
  cols=2
)
x<-dev.off()
x<-autocrop("hollister_microcystin_fig2.jpg",border = 25, 
            outfile = "hollister_microcystin_fig2.jpg",
            width = 6.1,
            res = 450)
```

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{hollister_microcystin_fig2.jpg}
\caption{\label{fig:multi_cp_plot}Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. A.) Plot for USEPA Child (0.3 $\mu$g/L). B.) Plot for WHO Drinking (1 $\mu$g/L). C.) Plot for USEPA Adult (1.6 $\mu$g/L). D.) Plot for WHO Recreational (2 $\mu$g/L).  }
\end{figure}

@@

```{r microcystin_levels,echo=FALSE,results='asis'}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "USEPA",
                    "USEPA")
type_of_stnd <- c("Recreational: Low Prob. of Effect",
                  "Recreational: Moderate Prob. of Effect",
                  "Recreational: High Prob. of Effect",
                  "Recreational: Very High Prob. of Effect",
                  "Drinking Water",
                  "Child Drinking Water Advisory",
                  "Adult Drinking Water Advisory")
concentration <- c("2-4 $mu$g/L",
                   "10-20 $mu$g/L",
                   "20-2000 $mu$g/L",
                   ">2000 $mu$g/L",
                   "1 $mu$g/L",
                   "0.3 $mu$g/L",
                   "1.6 $mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
#knitr::kable(mc_conc_table,format="latex")
print(xtable::xtable(mc_conc_table,
                     label="microcystin_levels",
                     caption="Various suggested microcystin-LR health advisory 
                     concentrations."), 
      include.rownames=FALSE, comment = FALSE,caption.placement = "top")
```

```{r mc_chla_table, results='asis', echo=FALSE}
mc_chla_tbl <- data.frame(seq(0.1,0.9,0.1),mc_chla)
names(mc_chla_tbl)<-c("Cond. Probability","USEPA Child", "WHO Drink", 
                      "USEPA Adult", "WHO Recreational")
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
#knitr::kable(mc_chla_tbl,format="latex")
print(xtable::xtable(mc_chla_tbl,
                     label="mc_chla_table",
                     caption="Chlorophyll \\textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration."),
      include.rownames = FALSE, comment = FALSE,caption.placement = "top")
```

```{r child_conmat_table, results='asis', echo=FALSE}
#knitr::kable(child_conmat,format="latex")
print(xtable::xtable(child_conmat,
                     label="child_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA childrens drinking water advisory."),
      include.rownames = FALSE, comment = FALSE,caption.placement = "top")
```

```{r who_drink_conmat_table, results='asis', echo=FALSE}
#knitr::kable(who_drink_conmat,format="latex")
print(xtable::xtable(who_drink_conmat,
                     label="who_drink_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory."),
      include.rownames = FALSE, comment = FALSE,caption.placement = "top")
```

```{r adult_conmat_table, results='asis', echo=FALSE}
#knitr::kable(adult_conmat,format="latex")
print(xtable::xtable(adult_conmat,
                     label="adult_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA adult drinking water advisory."),
      include.rownames = FALSE, comment = FALSE,caption.placement = "top")
```

```{r who_rec_conmat_table, results='asis', echo=FALSE}
#knitr::kable(who_rec_conmat,format="latex")
print(xtable::xtable(who_rec_conmat,
                     label="who_rec_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory."),
      include.rownames = FALSE, comment = FALSE,caption.placement = "top")
```

\newpage
\twocolumn

>>>>

We used the 2007 NLA chlorophyll *a* and microcystin-LR concentration data [@usepa2009national, [NLA](http://www2.epa.gov/national-aquatic-resource-surveys/national-lakes-assessment)]. These data represent a snapshot of water quality from the summer of 2007 for the conterminous United States and were collected as part of an ongoing probabilistic monitoring program [@usepa2009national]. Data on chlorophyll *a* and microcystin-LR concentrations are available for `r nrow(na.omit(data.frame(nla_dat$CHLA,nla_dat$MCYST_TL_UGL)))` lakes.

@@

```{r epa_child_cp_plot, echo=FALSE, fig.width=6, fig.cap="",warning=FALSE,message=FALSE}
jpeg(filename = "hollister_microcystin_fig1.jpg",
       res = 450,
       width = 7.82,
       height = 6.8,
       units = "in")
multiplot(
  plot_cp(epa_child_cp,x = "Log 10 Chlorophyll", 
          y = "Conditional Probability",
          title="A."),
  plot_cp(who_drink_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="B."),
  plot_cp(epa_adult_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="C."),
  plot_cp(who_rec_low1_cp, x = "Log 10 Chlorophyll", 
          y = "Conditional Probability", 
          title="D."),
  cols=2
)
x<-dev.off()
x<-autocrop("hollister_microcystin_fig1.jpg",border = 25, 
            outfile = "hollister_microcystin_fig1.jpg",
            width = 6.1,
            res = 450)
```

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{hollister_microcystin_fig1.jpg}
\caption{\label{fig:multi_cp_plot}Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. A.) Plot for USEPA Child (0.3 $\mu$g/L). B.) Plot for WHO Drinking (1 $\mu$g/L). C.) Plot for USEPA Adult (1.6 $\mu$g/L). D.) Plot for WHO Recreational (2 $\mu$g/L).  }
\end{figure}

@@

```{r microcystin_levels,echo=FALSE,results='asis'}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "USEPA",
                    "USEPA")
type_of_stnd <- c("Recreational: Low Prob. of Effect",
                  "Recreational: Moderate Prob. of Effect",
                  "Recreational: High Prob. of Effect",
                  "Recreational: Very High Prob. of Effect",
                  "Drinking Water",
                  "Child Drinking Water Advisory",
                  "Adult Drinking Water Advisory")
concentration <- c("2-4 $\\mu$g/L",
                   "10-20 $\\mu$g/L",
                   "20-2000 $\\mu$g/L",
                   ">2000 $\\mu$g/L",
                   "1 $\\mu$g/L",
                   "0.3 $\\mu$g/L",
                   "1.6 $\\mu$g/L")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
#pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
#knitr::kable(mc_conc_table,format="latex")
print(xtable::xtable(mc_conc_table,
                     label="microcystin_levels",
                     caption="Various suggested microcystin-LR health advisory 
                     concentrations from the USEPA and World Health Organization."), 
      include.rownames=FALSE, comment = FALSE,caption.placement = "top",
      latex.environments = NULL,sanitize.text.function=identity)
```

```{r mc_chla_table, results='asis', echo=FALSE}
mc_chla_tbl <- data.frame(seq(0.1,0.9,0.1),mc_chla)
names(mc_chla_tbl)<-c("Cond. Probability","USEPA Child", "WHO Drink", 
                      "USEPA Adult", "WHO Recreational")
#pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
#knitr::kable(mc_chla_tbl,format="latex")
print(xtable::xtable(mc_chla_tbl,
                     label="mc_chla_table",
                     caption="Chlorophyll \\textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration."),
      include.rownames = FALSE, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r child_conmat_table, results='asis', echo=FALSE}
#knitr::kable(child_conmat,format="latex")
print(xtable::xtable(child_conmat,
                     label="child_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA childrens drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r who_drink_conmat_table, results='asis', echo=FALSE}
#knitr::kable(who_drink_conmat,format="latex")
print(xtable::xtable(who_drink_conmat,
                     label="who_drink_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r adult_conmat_table, results='asis', echo=FALSE}
#knitr::kable(adult_conmat,format="latex")
print(xtable::xtable(adult_conmat,
                     label="adult_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA adult drinking water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

```{r who_rec_conmat_table, results='asis', echo=FALSE}
#knitr::kable(who_rec_conmat,format="latex")
print(xtable::xtable(who_rec_conmat,
                     label="who_rec_conmat_table",
                     caption="Confusion matrix comparing chlorophyll \\textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory."),
      include.rownames = T, comment = FALSE,caption.placement = "top",latex.environments = NULL)
```

\twocolumn

### 2016-01-25 manuscript/f1000_submission/manuscript.tex
version (almost) ready to submit to f1000

We used the 2007 NLA chlorophyll \emph{a} and microcystin-LR
concentration data {[}13{]}. These data represent a snapshot of water
quality from the summer of 2007 for the conterminous United States and
were collected as part of an ongoing probabilistic monitoring program
{[}13{]}. Data on chlorophyll \emph{a} and microcystin-LR concentrations
are available for lakes.

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{hollister_microcystin_fig2.jpg}
\caption{\label{fig:multi_cp_plot}Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. A.) Plot for USEPA Child (0.3 $\mu$g/L). B.) Plot for WHO Drinking (1 $\mu$g/L). C.) Plot for USEPA Adult (1.6 $\mu$g/L). D.) Plot for WHO Recreational (2 $\mu$g/L).  }
\end{figure}

@@

\begin{table}[ht]
\centering
\caption{Various suggested microcystin-LR health advisory 
                     concentrations.} 
\label{microcystin_levels}
\begin{tabular}{lll}
  \hline
Source & Type & Concentration \\ 
  \hline
USEPA & Adult Drinking Water Advisory & 1.6 \$mu\$g/L \\ 
  USEPA & Child Drinking Water Advisory & 0.3 \$mu\$g/L \\ 
  WHO & Drinking Water & 1 \$mu\$g/L \\ 
  WHO & Recreational: High Prob. of Effect & 20-2000 \$mu\$g/L \\ 
  WHO & Recreational: Low Prob. of Effect & 2-4 \$mu\$g/L \\ 
  WHO & Recreational: Moderate Prob. of Effect & 10-20 \$mu\$g/L \\ 
  WHO & Recreational: Very High Prob. of Effect & $>$2000 \$mu\$g/L \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Chlorophyll \textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration.} 
\label{mc_chla_table}
\begin{tabular}{rrrrr}
  \hline
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO Recreational \\ 
  \hline
0.10 & 0.07 & 0.07 & 0.07 & 1.22 \\ 
  0.20 & 0.07 & 4.43 & 11.80 & 20.00 \\ 
  0.30 & 2.98 & 20.43 & 31.40 & 53.64 \\ 
  0.40 & 10.67 & 42.24 & 66.96 & 82.22 \\ 
  0.50 & 23.36 & 66.96 & 83.52 & 105.84 \\ 
  0.60 & 38.30 & 103.20 & 133.20 & 155.52 \\ 
  0.70 & 65.60 & 166.63 & 871.20 & 216.00 \\ 
  0.80 & 117.50 & 338.40 & 871.20 & 871.20 \\ 
  0.90 & 167.04 & 516.00 & 871.20 & 871.20 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA childrens drinking water advisory.} 
\label{child_conmat_table}
\begin{tabular}{rrr}
  \hline
Not Exceed & Exceed & Row Totals \\ 
  \hline
649 &  96 & 745 \\ 
  162 & 121 & 283 \\ 
  811 & 217 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory.} 
\label{who_drink_conmat_table}
\begin{tabular}{rrr}
  \hline
Not Exceed & Exceed & Row Totals \\ 
  \hline
839 &  77 & 916 \\ 
   68 &  44 & 112 \\ 
  907 & 121 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA adult drinking water advisory.} 
\label{adult_conmat_table}
\begin{tabular}{rrr}
  \hline
Not Exceed & Exceed & Row Totals \\ 
  \hline
883 &  57 & 940 \\ 
   54 &  34 &  88 \\ 
  937 &  91 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory.} 
\label{who_rec_conmat_table}
\begin{tabular}{rrr}
  \hline
Not Exceed & Exceed & Row Totals \\ 
  \hline
910 &  52 & 962 \\ 
   43 &  23 &  66 \\ 
  953 &  75 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\newpage
\twocolumn

@@

3. HABHRCA (2014) Harmful algal bloom and hypoxia research and control
amendments act of 2014. Available:
\url{https://www.congress.gov/113/bills/s1254/BILLS-113s1254enr.pdf}.

@@

6. USEPA (2015) Drinking water health advisory for the cyanobacterial
microcystin toxins. ePA-820R15100. Available:
\url{http://www2.epa.gov/sites/production/files/2015-06/documents/microcystins-report-2015.pdf}.

7. Organization WH (2003) Cyanobacterial toxins: Microcystin-lR in
drinking-water. background document for development of wHO guidelines
for drinking-water quality. geneva, switzerland. World Health
Organization, 2nd ed. Geneva.

8. Chorus EI, Bartram J (1999) Toxic cyanobacteria in water: A guide to
their public health consequences, monitoring and management.

@@

11. Pip E, Bowman L (2014) Microcystin and algal chlorophyll in relation
to nearshore nutrient concentrations in lake winnipeg, canada.
Environment and Pollution 3: p36.

@@

13. USEPA (2009) National lakes assessment: A collaborative survey of
the nation's lakes. ePA 841-r-09-001.

@@

15. Paul JF, McDonald ME (2005) Development of empirical, geographically
specific water quality criteria: A conditional probability analysis
approach. 41: 1211--1223.

16. Hollister JW, Walker HA, Paul JF (2008) CProb: A computational tool
for conducting conditional probability analysis. Journal of
environmental quality 37: 2392--2396.

>>>>

We used the 2007 NLA chlorophyll \emph{a} and microcystin-LR
concentration data {[}13{]}. These data represent a snapshot of water
quality from the summer of 2007 for the conterminous United States and
were collected as part of an ongoing probabilistic monitoring program
{[}13{]}. Data on chlorophyll \emph{a} and microcystin-LR concentrations
are available for 1028 lakes.

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{hollister_microcystin_fig1.jpg}
\caption{\label{fig:multi_cp_plot}Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. A.) Plot for USEPA Child (0.3 $\mu$g/L). B.) Plot for WHO Drinking (1 $\mu$g/L). C.) Plot for USEPA Adult (1.6 $\mu$g/L). D.) Plot for WHO Recreational (2 $\mu$g/L).  }
\end{figure}

@@

\begin{table}[ht]
\caption{Various suggested microcystin-LR health advisory 
                     concentrations from the USEPA and World Health Organization.} 
\label{microcystin_levels}
\begin{tabular}{lll}
  \hline
Source & Type & Concentration \\ 
  \hline
USEPA & Adult Drinking Water Advisory & 1.6 $\mu$g/L \\ 
  USEPA & Child Drinking Water Advisory & 0.3 $\mu$g/L \\ 
  WHO & Drinking Water & 1 $\mu$g/L \\ 
  WHO & Recreational: High Prob. of Effect & 20-2000 $\mu$g/L \\ 
  WHO & Recreational: Low Prob. of Effect & 2-4 $\mu$g/L \\ 
  WHO & Recreational: Moderate Prob. of Effect & 10-20 $\mu$g/L \\ 
  WHO & Recreational: Very High Prob. of Effect & >2000 $\mu$g/L \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Chlorophyll \textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration.} 
\label{mc_chla_table}
\begin{tabular}{rrrrr}
  \hline
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO Recreational \\ 
  \hline
0.10 & 0.07 & 0.07 & 0.07 & 1.22 \\ 
  0.20 & 0.07 & 4.43 & 11.80 & 20.00 \\ 
  0.30 & 2.98 & 20.43 & 31.40 & 53.64 \\ 
  0.40 & 10.67 & 42.24 & 66.96 & 82.22 \\ 
  0.50 & 23.36 & 66.96 & 83.52 & 105.84 \\ 
  0.60 & 38.30 & 103.20 & 133.20 & 155.52 \\ 
  0.70 & 65.60 & 166.63 & 871.20 & 216.00 \\ 
  0.80 & 117.50 & 338.40 & 871.20 & 871.20 \\ 
  0.90 & 167.04 & 516.00 & 871.20 & 871.20 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA childrens drinking water advisory.} 
\label{child_conmat_table}
\begin{tabular}{rrrr}
  \hline
 & Not Exceed & Exceed & Row Totals \\ 
  \hline
Not Exceed & 649 &  96 & 745 \\ 
  Exceed & 162 & 121 & 283 \\ 
  Column Totals & 811 & 217 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory.} 
\label{who_drink_conmat_table}
\begin{tabular}{rrrr}
  \hline
 & Not Exceed & Exceed & Row Totals \\ 
  \hline
Not Exceed & 839 &  77 & 916 \\ 
  Exceed &  68 &  44 & 112 \\ 
  Column Totals & 907 & 121 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA adult drinking water advisory.} 
\label{adult_conmat_table}
\begin{tabular}{rrrr}
  \hline
 & Not Exceed & Exceed & Row Totals \\ 
  \hline
Not Exceed & 883 &  57 & 940 \\ 
  Exceed &  54 &  34 &  88 \\ 
  Column Totals & 937 &  91 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory.} 
\label{who_rec_conmat_table}
\begin{tabular}{rrrr}
  \hline
 & Not Exceed & Exceed & Row Totals \\ 
  \hline
Not Exceed & 910 &  52 & 962 \\ 
  Exceed &  43 &  23 &  66 \\ 
  Column Totals & 953 &  75 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\twocolumn

@@

3. Bloom HA, Research H, Act CA (2014) Harmful Algal Bloom and Hypoxia
Research and Control Amendments Act of 2014. (S. 1254). Available:
\url{https://www.congress.gov/113/bills/s1254/BILLS-113s1254enr.pdf}.

@@

6. USEPA (2015) Drinking water health advisory for the cyanobacterial
microcystin toxins. EPA-820-R-15100. Available:
\url{http://www2.epa.gov/sites/production/files/2015-06/documents/microcystins-report-2015.pdf}.

7. World Health Organization (2003) Cyanobacterial toxins:
Microcystin-LR in drinking-water. Background document for development of
WHO guidelines for drinking-water quality. Geneva, Switzerland. World
Health Organization, 2nd ed. Geneva.

8. Chorus EI, Bartram J (1999) Toxic cyanobacteria in water: A guide to
their public health consequences, monitoring and management. World
Health Organization.

@@

11. Pip E, Bowman L (2014) Microcystin and algal chlorophyll in relation
to nearshore nutrient concentrations in Lake Winnipeg, Canada.
Environment and Pollution 3: p36.

@@

13. USEPA (2009) National lakes assessment: A collaborative survey of
the nation's lakes. EPA 841-R-09-001.

@@

15. Paul JF, McDonald ME (2005) Development of empirical, geographically
specific water quality criteria: A conditional probability analysis
approach. Journal of the American Water Resources Association 41:
1211--1223.

16. Hollister JW, Walker HA, Paul JF (2008) CProb: A computational tool
for conducting conditional probability analysis. Journal of
Environmental Quality 37: 2392--2396.
